quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-07-06 paper-quollr.Rmd
Added Figure title for algorithm plots

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)
library(plotly)
library(crosstalk)
library(htmltools)
#library(tools)

@@

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions (`r knitr::asis_output(if (knitr::is_html_output()) { "[Figure 2](#fig-algo-steps)"} else { "Figure \\@ref(fig:algo-steps)"})`). A detailed description of the algorithm can be found in **cite the methodology paper**.

```{r, eval=knitr::is_html_output()}

htmltools::browsable(
  tagList(
    tags$div(
      id = "fig-algo-steps",  # This is the anchor
      crosstalk::bscols(
        htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr 1fr 1fr 1fr; gap: 0;",
                       htmltools::div(style = "margin: 0; padding: 0;", scurve_umap_plt_int),
                       htmltools::div(style = "margin: 0; padding: 0;", hex_grid_poly_scurve_int),
                       htmltools::div(style = "margin: 0; padding: 0;", hex_centroids_scurve_int),
                       htmltools::div(style = "margin: 0; padding: 0;", wireframe_scurve_int),
                       htmltools::div(
                         style = "margin-top: 13px;t",
                         scurve_umap_model_vis_n
                       )),
        device = "xs"
      ),
      tags$p(tags$strong("Figure 2:"), "Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown.")
    )
  )
)
```

@@

Two derived constants are calculated to define the relative distances to the vertices. The horizontal and vertical offset is defined as $dx = \frac{a_1}{2}$, and $dy = \frac{a_1}{\sqrt{3}}$ repectively. A vertical spacing factor $v = \frac{a_1}{2\sqrt{3}}$ refines vertical placement in staggered rows.

>>>>

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)
library(plotly)
library(crosstalk)
library(htmltools)
library(crosstalk)
#library(tools)

@@

Our algorithm includes the following steps: (1) scaling the NLDR data, (2) computing configurations of a hexagon grid, (3) binning the data, (4) obtaining the centroids of each bin, (5) indicating neighboring bins with line segments that connect the centroids, and (6) lifting the model into high dimensions (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:algo-step-html)"} else { "Figure \\@ref(fig:algo-steps)"})`). A detailed description of the algorithm can be found in **cite the methodology paper**.

```{r algo-step-html, eval=knitr::is_html_output(), out.width="100%", fig.height=5, fig.width=25, fig.pos='H', fig.cap="Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown."}

algofig <- crosstalk::bscols(
        htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr 1fr 1fr 1fr; gap: 0;",
                       htmltools::div(style = "margin: 0; padding: 0;", scurve_umap_plt_int),
                       htmltools::div(style = "margin: 0; padding: 0;", hex_grid_poly_scurve_int),
                       htmltools::div(style = "margin: 0; padding: 0;", hex_centroids_scurve_int),
                       htmltools::div(style = "margin: 0; padding: 0;", wireframe_scurve_int),
                       htmltools::div(
                         style = "margin-top: 13px;t",
                         scurve_umap_model_vis_n
                       )),
        device = "xs"
      )

class(algofig) <- c(class(algofig), "htmlwidget")

algofig
```

@@

Two derived constants are calculated to define the relative distances to the vertices. The horizontal and vertical offset is defined as $dx = a_1/2$, and $dy = a_1/\sqrt{3}$ repectively. A vertical spacing factor $v = a_1/2\sqrt{3}$ refines vertical placement in staggered rows.

### 2025-07-06 paper-quollr.tex
Added Figure title for algorithm plots

Two derived constants are calculated to define the relative distances to the vertices. The horizontal and vertical offset is defined as \(dx = \frac{a_1}{2}\), and \(dy = \frac{a_1}{\sqrt{3}}\) repectively. A vertical spacing factor \(v = \frac{a_1}{2\sqrt{3}}\) refines vertical placement in staggered rows.

>>>>

Two derived constants are calculated to define the relative distances to the vertices. The horizontal and vertical offset is defined as \(dx = a_1/2\), and \(dy = a_1/\sqrt{3}\) repectively. A vertical spacing factor \(v = a_1/2\sqrt{3}\) refines vertical placement in staggered rows.
